Manuscript draft

### 2024-04-17 manuscript.rmd
updated with more of the results

```{r include = FALSE}
library(tidyverse)
library(here)
library(targets)
library(patchwork)
library(ggeffects)
library(gtsummary)
theme_set(theme_classic())
tar_config_set(store = here::here('_targets'))
#source(here("scripts/04.0_mixedModels.R"))
tar_load(cleaned_r)
tar_load(joined0_r)
tar_load(downsampled_10min_forSocial_r)
tar_load(downsampled_10min_r)
tar_load(cc)
tar_load(linked)
tar_load(deg_mod)
tar_load(deg_z_mod)
tar_load(str_mod)
tar_load(str_z_mod)
tar_load(situcolors)
tar_load(seasoncolors)
tar_load(movement_corr)
tar_load(space_corr)
tar_load(roost_corr)
```

@@

```{r message = FALSE}
linked %>%
  select(seasonUnique, situ, z_deg, z_str) %>%
  ungroup() %>%
  pivot_longer(cols = contains("z_"), names_to = "measure", values_to = "z") %>%
  ggplot(aes(x = z, col = situ, group = interaction(seasonUnique, measure, situ)))+
  geom_density(aes(linetype = measure))+
  facet_wrap(~measure*situ, scales = "free")+
  geom_vline(aes(xintercept = 0), col = "red")+
  scale_color_manual(name = "Situation", values = c(cc$feedingColor, cc$flightColor, cc$roostingColor))+
  theme_classic()+
  theme(axis.title.y = element_blank())+
  xlab("Z-score")
```

@@

@@

>>>>

```{r include = FALSE}
library(tidyverse)
library(here)
library(targets)
library(patchwork)
library(ggeffects)
library(gtsummary)
theme_set(theme_classic())
tar_config_set(store = here::here('_targets'))
#source(here("scripts/04.0_mixedModels.R"))
tar_load(cleaned_r)
tar_load(joined0_r)
tar_load(downsampled_10min_forSocial_r)
tar_load(downsampled_10min_r)
tar_load(cc)
tar_load(linked)
tar_load(deg_mod)
tar_load(deg_z_mod)
tar_load(str_mod)
tar_load(str_z_mod)
tar_load(situcolors)
tar_load(seasoncolors)
tar_load(movement_corr)
tar_load(space_corr)
tar_load(roost_corr)

effplot <- function(model, terms, dataset, pointX, pointY, colvar, legendTitle, values, ylab, xlab){
  dat <- as.data.frame(ggeffect(model, terms = terms))

  if(length(terms) > 1){
    plt <- ggplot(dat, aes(x, predicted)) +
      geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2, linewidth = 0.6, show.legend = F)+
      geom_point(data = dataset %>% mutate("group" = .data[[colvar]]), 
                 aes(.data[[pointX]], .data[[pointY]], col = group), alpha = 0.5)+
      geom_line(aes(col = group), linewidth = 1) +
      facet_wrap(~group, scales = "free_y")+
      scale_color_manual(legendTitle, values = values) + 
      scale_fill_manual(legendTitle, values = values) + 
      ylab(ylab) + xlab(xlab)
  }else{
    plt <- ggplot(dat, aes(x, predicted)) +
      geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, linewidth = 0.6, show.legend = F)+
      geom_point(data = dataset %>% mutate("group" = .data[[colvar]]), 
                 aes(.data[[pointX]], .data[[pointY]], col = group), alpha = 0.5)+
      geom_line(linewidth = 1) +
      facet_wrap(~group, scales = "free_y")+
      scale_color_manual(legendTitle, values = values) + 
      ylab(ylab) + xlab(xlab)
  }
  return(plt)
}

emtplot <- function(model, specs, var, values, ylab, xlab){
  dat <- as.data.frame(emmeans::emtrends(model, specs, var))
  lower <- ifelse("lower.CL" %in% names(dat), "lower.CL", "asymp.LCL")
  upper <- ifelse("upper.CL" %in% names(dat), "upper.CL", "asymp.UCL")
  plt <- dat %>% ggplot(aes(.data[[specs]], 
                            .data[[paste0(var, ".", "trend")]], 
                            col = .data[[specs]])) + 
    geom_point(size = 6) +
    geom_errorbar(aes(x = .data[[specs]], 
                      ymin = .data[[lower]], 
                      ymax = .data[[upper]]), 
                  width = 0, linewidth = 2)+geom_hline(aes(yintercept = 0), 
                                                       linetype = 2)+
    scale_color_manual(values = values)+ 
    theme(legend.position = "none") + ylab(ylab)+ xlab(xlab) + coord_flip()
  return(plt)
}
```

@@

```{r message = FALSE, out.width = "100%"}
linked %>%
  select(seasonUnique, situ, z_deg, z_str) %>%
  ungroup() %>%
  pivot_longer(cols = contains("z_"), names_to = "measure", values_to = "z") %>%
  ggplot(aes(x = z, col = situ, group = interaction(seasonUnique, measure, situ)))+
  geom_density(aes(linetype = measure))+
  facet_wrap(~measure*situ, scales = "free")+
  geom_vline(aes(xintercept = 0), col = "red")+
  scale_color_manual(name = "Situation", values = c(cc$feedingColor, cc$flightColor, cc$roostingColor))+
  theme_classic()+
  theme(axis.title.y = element_blank())+
  xlab("Z-score")
```

@@

Preferential degree (i.e. degree z-score) was significantly associated with space use and roost diversification, but not with movement. Vultures that used more space (i.e. those with larger home ranges and larger proportional core areas) had a co-flight degree that deviated more from random (i.e. more preferential degree) than those with smaller space use. By contrast, co-roosting degree deviated less, not more, from random for wide-ranging vultures. [FIGURE] (Co-roosting degree showed a similar trend to co-flight, though it was only marginally significant).

```{r fig.cap = "Degree z-scores", out.width = "100%"}
deg_z_situ_space_emt_P <- effplot(model = deg_z_mod, terms = c("space_use", "situ"), 
                            dataset = linked, pointX = "space_use", 
                            pointY = "z_deg", col = "situ", 
                            legendTitle = "Situation", values = situcolors, 
                            ylab = "Degree (z-score)", xlab = "Space use (log)")

deg_z_situ_space_P <- emtplot(model = deg_z_mod, specs = "situ", 
                                var = "space_use", values = situcolors, 
                                ylab = "Space use effect (Degree z-scores)", 
                                xlab = "Situation")

deg_z_situ_space_emt_P + deg_z_situ_space_P + plot_layout(widths = c(4, 1), guides = "collect") & theme_classic()
```

Meanwhile, roost diversification negatively predicted preferential degree in all social situations, with no significant difference in effect magnitude between situations. Vultures with more unique roosts, more roost switching, and/or a higher diversity of roosts differed less from the degree expected by chance than those with lower roost diversification.

```{r}
deg_z_roost_P <- effplot(model = deg_z_mod, terms = c("roost_div", "situ"), 
                       dataset = linked, pointX = "roost_div", 
                       pointY = "z_deg", col = "situ", 
                       legendTitle = "Situation", values = situcolors, 
                       ylab = "Degree (z-score)", xlab = "Roost diversification")
deg_z_roost_P & theme_classic()
```

@@

The relationships were very similar for strength. Preferential strength in the co-flight and co-feeding networks was positively associated with space use, with wider-ranging vultures' strength deviating the most from random. Meanwhile, the opposite was once again true for the co-roosting network. Vultures with smaller ranges deviated singificantly more from random than those with larger ranges.
